cardinalR: Generating interesting high-dimensional data structures

### 2025-05-04 paper-cardinalR.Rmd
Added S-curve hole description

@@

>>>>

To simulate a variant of the S-curve structure with a removed region ("hole"), we define the function `gen_scurvehole(n, p)`. This function produces `n` observations in a $p$-dimensional space where the first three dimensions describe the S-curve manifold, and remaining dimensions add low-variance Gaussian noise. A subset of observations near a designated anchor point is excluded to introduce a hole in the manifold.

To simulate missing regions on the manifold, a fixed anchor point $(0, 1, 0, \ldots)$ is defined in $p$-dimensional space. All observations within a Euclidean distance of $\sqrt{0.3} \approx 0.5477$ from the anchor are removed:

$$
\text{remove if} \quad \sum_{j=1}^p (X_j - a_j)^2 \leq 0.3
$$.

This exclusion creates a hole in the manifold centered near the middle vertical region of the S-curve.

@@

- Scurve with a hole allowing for evaluation of how well algorithms handle incomplete manifolds or missing local structure.
